The Resurgence of the Linear Optics Interferometer --- Recent Advances \& Applications

### 2017-01-09 paper.tex
added ack
Added a new paragraph to math section.

\newcommand{\sihui}[1]{{\color{Orchid}{#1}}}
\newcommand{\peter}[1]{{\color{YellowGreen}{#1}}}
\newcommand{\comment}[1]{{\color{blue}{#1}}}

@@

\section{Mathematical background}

\comment{Mathematical representation for LO networks, and very basic background on quantum optics}

@@

\begin{acknowledgments}
\end{acknowledgments}

>>>>

\newcommand{\sihui}[1]{{\color{Orchid}{#1}}}
\newcommand{\peter}[1]{{\color{YellowGreen}{#1}}}
\newcommand{\comment}[1]{{\color{blue}{#1}}}
\newcommand{\ah}{\hat{a}}
\newcommand{\adagh}{\hat{a}^\dag}

@@

\section{Mathematical background}
\comment{Mathematical representation for LO networks, and very basic background on quantum optics}\\
\sihui{A idealized single photon in a quantum interferometer is described by its creation operator $\adagh_{j,\alpha}$, where $j$ is the path label and $\alpha$ is a quantum number that describes any internal degrees of freedom of the photon. The creation and annihilation operators satisfy the bosonic comutator relationship $[\ah_{j,\alpha},\adagh_{k,\beta}]=\delta_{j,k}\delta_{\alpha,\beta}$. When multiple photons are present, they experience quantum interference when both quantum labels are the same.

A linear optical interferometer}

@@

\begin{acknowledgments}
P.P.R. is funded by an ARC Future Fellowship (project FT160100397).
\end{acknowledgments}
